\documentclass[]{deedy-resume-openfont}



\usepackage{comment} % Allow for commenting out blocks of code
\usepackage{makecell}
\usepackage[hang,flushmargin]{footmisc} % Format footnotes
\usepackage{longtable} % Allow "longtable" format, which lets long tables span multiple pages automatically
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{rotating}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage[capposition=top]{floatrow} % Helps center tables somehow
\usepackage{pdflscape} % Allow some pages to be landscape
\usepackage{setspace} % Allow for double spacing 
\usepackage[justification=centering,large]{caption}
\usepackage{charter} % font
\usepackage{needspace}
\usepackage{indentfirst}\setlength\parindent{1cm} %indent first paragraph of sections
\usepackage{hyperref}
\usepackage{soul}
\usepackage{etoolbox}

% Prevent orphaned headings (keep titles with at least a couple lines of content)
\pretocmd{\section}{\needspace{10\baselineskip}}{}{}
\pretocmd{\subsection}{\needspace{5\baselineskip}}{}{}
\ifdef{\runsubsection}{\pretocmd{\runsubsection}{\needspace{4\baselineskip}}{}{}{}}{}

\renewcommand{\arraystretch}{1.3}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage[english]{babel}
\usepackage{inputenc}

%\setlist[enumerate]{noitemsep}
\setlist[enumerate,1]{leftmargin=*}



 
\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
 
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{NICHOLAS J.}{HALLMAN}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EMPLOYMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Employment}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}
\begin{minipage}[t]{0.5\textwidth} 

\subsection{The University of Texas Austin}
\location{2023 - Present | Associate Professor (tenured)}
\location{2016 - 2023 | Assistant Professor}
\sectionsep

\subsection{Salem Center for Policy}
\location{2023 - Present | Senior Scholar for AI Initiatives}
\sectionsep

\subsection{Paideum Education} 
\location{2025 - Present | Founder | \href{https://paideum.com}{\textit{\ul{Paideum.com}}}}

\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\subsection{CAS Center for Auditing}
\location{2026 - Present \hspace{.08cm}| Head of Data and AI Initiatives}
\sectionsep

\subsection{Deloitte}
\location{2011 – 2012 \hspace{.08cm}| Senior Auditor}
\location{2009 – 2011 | Staff Auditor}

\end{minipage} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education \& Certification}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}
\begin{minipage}[t]{0.5\textwidth} 

\subsection{University of Missouri Columbia}
\descript{PhD in Accountancy}
\location{May 2016}

\sectionsep

\subsection{Certified Public Accountant}
\descript{North Carolina (Inactive)}

\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\subsection{Appalachian State University }
\descript{BS and MS in Accountancy}
\location{August 2009}
\end{minipage} 




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
\section{Research}
\vspace*{-.25cm}
\rule{\textwidth}{0.1pt}

\vspace*{.15cm}
\subsection{Peer Reviewed Publications} 
\vspace*{-.4cm}

\begin{longtable}{>{\raggedright\arraybackslash}p{.5cm}p{16.9cm}}
\endfirsthead
\multicolumn{2}{l}{\textit{(Peer reviewed publications continued from previous page)}}
\endhead
\multicolumn{2}{r}{\textit{(Peer reviewed publications continued on next page)}}
\endfoot
\endlastfoot
    1. & Gender Disparities in Auditing. With Jade Chen and Jayanthi Sunder. Conditionally accepted, \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4678211}{\textit{\ul{Review of Accounting Studies}}}. \\
    2. & Analyst coverage and syndicated lending. With John Howe and Wei Wang. \href{https://doi.org/10.1007/s11142-022-09670-8}{\textit{\ul{Review of Accounting Studies}}}, 2023. \\
    3. & Audit implications of non-GAAP reporting. With Anne Thompson and Jaime Schmidt. \href{https://doi.org/10.1111/1475-679X.12433}{\textit{\ul{Journal of Accounting Research}}}, 2022. \\
    4. & How do auditors respond to competition? Evidence from the bidding process. With Antonis Kartapanis and Jaime Schmidt. \href{https://doi.org/10.1016/j.jacceco.2021.101475}{\textit{\ul{Journal of Accounting and Economics}}}, 2022. \\
    5. & Does distance matter? An investigation of partners who audit distant clients and the effects on audit quality. With Jere Francis and Nargess Golshan. \href{https://doi.org/10.1111/1911-3846.12744}{\textit{\ul{Contemporary Accounting Research}}}, 2022. \\
    6. & A matter of appearances: How does auditing expertise benefit audit committees when selecting auditors? With Matthew Baugh and Steven Kachelmeier. \href{https://doi.org/10.1111/1911-3846.12736}{\textit{\ul{Contemporary Accounting Research}}}, 2022. Zach Kowaleski's favorite accounting paper (last confirmed in 2024). \\
    7. & On the relation between insider trading and going concern opinions. With Andrew Imdieke, Kyonghee Kim, and Raynolde Pereira. \href{https://doi.org/10.2308/ajpt-52592}{\textit{\ul{AUDITING: A Journal of Practice and Theory}}}, 2020. \\
    8. & The geographic decentralization of audit firms and audit quality. With Matthew Beck and Joshua Gunn. \href{https://doi.org/10.1016/j.jacceco.2019.101234}{\textit{\ul{Journal of Accounting and Economics}}}, 2019. \\
    9. & Awareness of SEC enforcement and auditor reporting decisions. With Mark DeFond and Jere Francis. \href{https://doi.org/10.1111/1911-3846.12352}{\textit{\ul{Contemporary Accounting Research}}}, 2018. \\
    10. & State pension liabilities and credit assessments. With Inder Khurana. \href{https://doi.org/10.2308/acch-51213}{\textit{\ul{Accounting Horizons}}}, 2015. \\
\end{longtable}


\vspace*{-.25cm}
\subsection{Working Papers} 
\vspace*{-.4cm}
%\begin{longtable}{l}
\begin{longtable}{>{\raggedright\arraybackslash}p{.5cm}p{16.9cm}}

\endfirsthead

\multicolumn{2}{l}{\textit{Current projects continued from previous page}}
\endhead

\multicolumn{2}{r}{\textit{Current projects continued on next page}}
\endfoot

\endlastfoot

    1. & Are audit fees discounted by successor auditors? With Jaime J. Schmidt. \href{https://dx.doi.org/10.2139/ssrn.4085798}{\underline{SSRN}}. \\

    2. & Audited non-GAAP earnings. With Anne Thompson and Jaime Schmidt. \href{https://dx.doi.org/10.2139/ssrn.4861966}{\underline{SSRN}}. \\

    3. & International PCAOB Inspections and the Decline in Foreign Listings to the U.S. With Shuping Chen and Albert Wang. \href{http://dx.doi.org/10.2139/ssrn.5700522}{\underline{SSRN}}. \\
    

\end{longtable}

\needspace{6\baselineskip}
\vspace*{-.25cm}
\subsection{Other Work}
\vspace*{-.4cm}
\begin{longtable}{>{\raggedright\arraybackslash}p{.5cm}p{16.9cm}}

\endfirsthead

\multicolumn{2}{l}{\textit{Other work continued from previous page}}
\endhead

\multicolumn{2}{r}{\textit{Other work continued on next page}}
\endfoot

\endlastfoot

    1. & What the Best AI Users Do Differently? With Zach Kowaleski, Anu Puvvada, and Jaime Schmidt (\href{https://hbr.org/2026/03/what-the-best-ai-users-do-differently-and-how-to-level-up-all-of-your-employees}{\underline{HBR}, 2026}) \\

    2. & What Would Friedman Say? Introducing Friedman.ai (\href{https://whatwouldfriedmansay.substack.com/p/introducing-friedmanai}{\underline{Substack}, 2024}) \\
    
    
    

\end{longtable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INVITED PRESENTATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\needspace{5\baselineskip}
\section{Invited Presentations}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}

\begin{minipage}[t]{0.5\textwidth} 

\subsection{Conferences}
AAA Audit PhD Consortium (2026) \\
Bretton Woods Accounting and Finance Conference (2025) \\
Swiss Accounting Research Alpine Camp (2025) \\
AAA/Deloitte Foundation/J. Michael Cook \\
\hspace*{.4cm} Doctoral Consortium (2024) \\ 
Business and Accounting Retreat (2024) \\ 
Illinois Symposium on Audit Research (2018, 2024) \\
ISAR (2015, 2017, 2018, 2019, 2024 - AI Panel) \\
Audit \& Assurance Conference in Edinburgh (2023) \\
Texas Lone Star Conference (2022) \\
Contemporary Accounting Research Conference (2020) \\
PCAOB/TAR Auditing and Capital Markets (2019) \\
KU Audit Symposium (2016, 2018) \\
AAA – Audit Midyear Meeting (2015, 2016, 2018) \\
AAA – Annual Meeting (2013, 2014, 2015, 2017, 2018) \\
AAA – FARS Midyear Meeting (2014) 



\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\subsection{Workshops}
University of Kentucky (2026, scheduled) \\
University of Arizona (2026) \\
Michigan State University (2025) \\
University of Texas at San Antonio (2025) \\
Arizona State University (2024) \\ 
University of Pittsburgh (2024) \\
University of Oklahoma (2023) \\
Penn State University (2023) \\
Temple University (2022) \\
University of Colorado Boulder (2019) \\
University of Illinois Champaign Urbana (2019, 2016) \\
Texas A\&M University (2016) \\
Northeastern University (2016) \\
Tulane University (2016) \\
University of Illinois Chicago (2015) \\
University of Arkansas (2015) \\

\end{minipage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Service}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}
\begin{minipage}[t]{0.5\textwidth}

\subsection{Associate Editor Positions}
Accounting Open (2025 - Present)
\sectionsep

\subsection{Editorial Boards}
Review of Accounting Studies (2026 - Present) \\
Contemporary Accounting Research (2023 - Present) \\
The Accounting Review (2021 - Present) \\
Auditing: A Journal of Practice \& Theory (2017 - 2026)
\sectionsep

\subsection{Ad Hoc Journal Referee}
Management Science \\
Journal of Accounting Research \\
Journal of Accounting and Economics \\
Accounting, Organizations, and Society \\
European Accounting Review \\
Accounting Horizons \\
Journal of Accounting, Auditing, and Finance \\
International Journal of Auditing \\
Applied Economics
\sectionsep

\subsection{Dissertation Committees}
Dorothy Dickmann, Chair (2025) \\
Minjae Kim (2024) \\
Ryan Ballestero (2021) 
\sectionsep


\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 




\subsection{Other Committees at McCombs}
Accounting Department Faculty Recruiting Committee \\
\hspace*{.4cm} Chair (2025) \\
Accounting Curriculum Review and Revision Committee \\ 
\hspace*{.4cm} Co-chair (2022-2023)\\
Accounting PhD Evaluation and Continuation Committee \\ 
\hspace*{.4cm} (2022-2023)\\
Executive Committee for the C. Aubrey Smith Center 
for \\ 
\hspace*{.4cm} Auditing Education \& Research (2023 - Present) \\
Accounting Department Strategic Plan Task Force (2025) 
\sectionsep

\subsection{Other Service}
Austin Fencers Club Board Member (2026-Present) \\
Auditing Track Chair of Hawaiian Accounting Research \\ \hspace*{.4cm} Conference (2025, 2026, 2027) \\ 
Faculty Mentor, AAA/Deloitte/J. Michael Cook Doctoral \\ \hspace*{.4cm} Consortium (2024) \\
Faculty Mentor, Auditing Doctoral Consortium \\ \hspace*{.4cm}(2021, 2026) \\
Scientific Committee European Accounting Association \\ 
\hspace*{.4cm} Congress (2020 and 2021) \\
McCombs peer teaching observer (Spring 2023, Fall 2023,  \\ 
\hspace*{.4cm} Spring 2024, Fall 2024, Spring 2025, Spring 2026)



\sectionsep

\end{minipage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TEACHING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}
\begin{minipage}[t]{0.5\textwidth} 

\runsubsection{Coding and Data Analytics for Accountants} \location{}
University of Texas Austin:\\
\hspace*{.4cm} Fall 2025 (Overall Instructor Rating: 4.5/5.0) \\
\hspace*{.4cm} Fall 2024 (Overall Instructor Rating: 4.7/5.0) \\
\hspace*{.4cm} Fall 2023 (Overall Instructor Rating: 4.9/5.0) \\
\hspace*{.4cm} Fall 2022 (Overall Instructor Rating: 4.6/5.0) \\
\sectionsep

\runsubsection{Introduction to Financial Accounting} \location{}
University of Missouri Columbia:\\
\hspace*{.4cm} Summer 2015 (Overall Instructor Rating: 4.4/5.0) \\
\hspace*{.4cm} Summer 2014 (Overall Instructor Rating: 4.5/5.0) \\
\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 

\runsubsection{Auditing and Assurance Services} \location{}
University of Texas Austin:\\
\hspace*{.4cm} Spring 2021 (Overall Instructor Rating: 4.8/5.0) \\
\hspace*{.4cm} Spring 2020 (Overall Instructor Rating: 4.8/5.0) \\
\hspace*{.4cm} Spring 2019 (Overall Instructor Rating: 4.5/5.0) \\
\hspace*{.4cm} Spring 2018 (Overall Instructor Rating: 4.6/5.0) \\
\hspace*{.4cm} Spring 2017 (Overall Instructor Rating: 4.5/5.0) \\
University of Missouri Columbia:\\
\hspace*{.4cm} Spring 2015 (Overall Instructor Rating: 4.5/5.0) \\
\sectionsep


\end{minipage} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards and Recognition
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and recognition}
\vspace*{-.25cm}
\rule{\textwidth}{0.3pt}

\begin{minipage}[t]{0.5\textwidth} 
\subsection{Awards}
Google Gemini Academic Research in AI Grant (2026) \\
CBA Foundation Advisory Council Award for Teaching \\ 
\hspace*{.4cm} Innovation - Winner (2025-2026) \\
CBA Foundation Advisory Council Award for Teaching \\ 
\hspace*{.4cm} Innovation - Nominated (2024-2025) \\
McCombs Research Excellence Grants (2023-2024) \\
Trammel/CBA Foundation Teaching Award For Assistant \\
\hspace*{.4cm} Professors - Winner (2022 - 2023) \\
CBA Foundation Research Excellence Award for Assistant \\
\hspace*{.4cm} Professors - Winner (2022 - 2023) \\
Trammel/CBA Foundation Teaching Award For Assistant \\
\hspace*{.4cm} Professors - Nominated (2021 - 2022) \\
CBA Foundation Research Excellence Award for Assistant \\
\hspace*{.4cm} Professors - Nominated (2021 - 2022) \\
McCombs Faculty Honor Role (2020)



\sectionsep

\end{minipage} 
\hfill
\begin{minipage}[t]{0.49\textwidth} 
\subsection{Media Mentions}

Why We Don’t Have More AI Power Users In The \\ \hspace*{.4cm} Age Of AI (\href{https://www.forbes.com/sites/joemckendrick/2026/03/22/why-we-dont-have-more-ai-power-users-in-the-age-of-ai/}{\underline{Forbes}, 2026}) \\
New study shows who is getting the most out of using \\ \hspace*{.4cm} AI for business (\href{https://www.tpr.org/news/2026-03-20/new-study-shows-who-is-getting-the-most-out-of-using-ai-for-business}{\underline{Texas Public Radio}, 2026}) \\
Behind the Data on AI at Work (\href{https://a7b1cb29-8eb2-4801-9ccb-e0eb899497ab.libsyn.com/behind-the-data-on-ai-at-work-with-dr-nick-hallman}{\underline{ATC Podcast}, 2026}) \\
How to Make AI Work for You (\href{https://whchronicle.com/episodes/how-to-make-ai-work-for-you/}{\underline{WH Chronicle}, 2026}) \\
Colleges Inject AI Into Accounting Programs to \\ \hspace*{.4cm} Increase Appeal (\href{https://news.bloombergtax.com/financial-accounting/colleges-inject-ai-into-accounting-programs-to-increase-appeal}{\underline{Bloomberg}, 2025}) \\
Salem Center launches new A.I. to recreate famous  \\ \hspace*{.4cm} economist Friedman’s perspective (\href{https://thedailytexan.com/2024/04/03/salem-center-launches-new-a-i-to-recreate-famous-economist-friedmans-perspective/}{\underline{Daily Texan}, 2024})
The Milton Friedman app isn't bad. Reading Friedman is \\ \hspace*{.4cm}much better (\href{https://financialpost.com/opinion/milton-friedman-app-isnt-bad-reading-friedman-much-better}{\underline{Financial Post}}, 2024) \\
SEC Chief Accountant Stresses Audit Committee Oversight  \\
\hspace*{.4cm} of ‘Other Auditors’ (\href{https://t.e2ma.net/click/qo491h/ejc7cb2/m9dsdw}{\underline{Financial Times - Agenda}}, 2023) \\
Proposed FASB Standard Would Reveal New Income \\
\hspace*{.4cm} Statement Details (\href{https://t.e2ma.net/click/qo491h/ejc7cb2/21esdw}{\underline{Financial Times - Agenda}}, 2023) \\
ChatGPT vs. CPA (\href{https://www.youtube.com/watch?v=PMAYckefB_w&t=1488s&pp=ygUMTmljayBIYWxsbWFu}{\underline{The Wealthability Podcast}}, 2023) \\
Auditing Committees Hire Handsome Partners \\ 
\hspace*{.4cm} (\href{https://medium.com/texas-mccombs/auditing-committees-hire-handsome-partners-29d99a33bf}{\underline{Medium}, 2022})


\end{minipage}


































\end{document}  \documentclass[]{article}

